---
name: "xxx your name xxx"
title: "Problem Set 1"
output: html_notebook
---

This problem set covers concepts from chapters 2.2-2.5 in *Humanities Data in R*, including:

* Calculator 
* Objects
* Numeric Vectors
* Logical Vectors
* Subsetting

As well as these concepts not covered in the book:

* Getting user input
* If statements

# Writing Code
For each of the following questions, write the code you need to solve the problem in the provided code block. Running each code block should result in a returned value-- either the result of a calcuation, or the printing of a variable. 

For example, rather than writing:

```{r}
x <- 1
```
you should write:

```{r}
x <- 1
x
```
Notice the difference between running these two code blocks.

Before submitting, be sure to run your code to make sure it is correct!

### Problems
1. Return the sum of all the numbers 1-100

```{r}

```

2. Create a variable called `x` and assign it any value between 1 and 10. Return the class of x.

```{r}

```

3. Multiply `x` by 2, and assign that new value to a variable called `y`.

```{r}

```

4. Check if the value of `x` is equal to the value of `y`.

```{r}

```

5. There is an operator in computing called "modulo" which tells you what the remainder is when a number is divided by the other. For example, 7 modulo 3 is 1, because 7/3 is 2 remainder 1. In R, we would write this as `7 %% 3`. Using the modulo operator, expand on the code provided to ask the user for a number, then returning "Your number is even!" if the number is even, or "Your number is odd!" if the number is odd. Refer back to the lab for help!

```{r}
ask <- function(){
  num <- readline("Enter a number: ")
  num <-  as.numeric(num)
  
  if(#your code here){
    print("Your number is even!")
  } else {
    print("Your number is odd!")
  }

}
ask()
```


#### Avengers Tenure

The following problems use a small subset of a dataset compiled by Five Thirty Eight on deaths in the Marvel universe's Avengers. You can access the full dataset [here](https://data.world/fivethirtyeight/avengers) and the article it was used for [here](https://fivethirtyeight.com/features/avengers-death-comics-age-of-ultron/).


| Alias            | Appearances | Year joined | Full member? | Died | Returned | 
|------------------|-------------|-------------|--------------|------|----------| 
| She-Hulk         | 55          | 1982        | No           | No   |  N/A     | 
| Agent Anti-Venom | 746         | 2012        | No           | No   |  N/A     | 
| The Wasp         | 1165        | 1963        | Yes          | Yes  | Yes      | 
| Storm            | 1598        | 2012        | Yes          | No   |  N/A     | 
| The Hulk         | 2089        | 1963        | Yes          | Yes  | Yes      | 
| Thor             | 2402        | 1963        | Yes          | Yes  | Yes      | 
| Iron Man         | 3068        | 1963        | Yes          | Yes  | Yes      | 
| Wolverine        | 3130        | 2005        | Yes          | Yes  | No       | 
| Spider-Man       | 4333        | 1990        | Yes          | Yes  | Yes      | 

6. How many years has it been since Wolverine joined the Avengers?

```{r}

```

7. How much longer has Spider-Man been an Avenger than Storm?

```{r}

```

8. On average, how many appearances has The Hulk made per year?

```{r}

```

9. Create a vector called `yearJoined` containing the year each character joined (in order of the table above).

```{r}

```

10. Using your `yearJoined` vector, calculate the number of years each character has been an Avenger, assuming all are currently still members. Save this new vector as `membershipLength`.

```{r}

```

11. Create two logical vectors: one for whether the characters have died, and one for whether they have returned. Call them `died` and `returned`, respectively. Note: N/A fields should be counted as `FALSE`.

```{r}

```

12. Using logical operators on the `died` and `returned` vectors, create a new logical vector called `stillAlive` that is `TRUE` for every character that is still alive (either never died or died and returned), and `FALSE` for everyone else.

```{r}

```

13. Using your `stillAlive` vector, return the total number of characters that are still alive.

```{r}

```

14. Death in comic books is a little wishy-washy, but let's say Wolverine's definitive death was in the 2014 "Death of Wolverine" storyline. Adjust Wolverine's entry in the `membershipLength` vector to account for his death. You should update only Wolverine's place in the existing vector; do not create a new vector or manually rewrite the entire existing one.

```{r}

```

15. Expand on the following code to ask the user to pick a character from a numbered list (provided) and tell them whether that character is still alive. Use your existing vectors to help with this! **Note:** `cat()` is another way of printing to the console-- it allows you to do linebreaks with `\n`.

```{r}
ask <- function(){
  cat("1. She-Hulk\n2. Agent Anti-Venom\n 3. The Wasp\n 4. Storm\n 5. The Hulk\n 6. Thor\n 7. Iron Man\n 8. Wolverine\n 9. Spider-Man
")
  
  
  #Ask the user to pick a number. Remember to cast their input as.numeric!

  
  #Return whether the character with that number is alive or dead.
  
  
}
  
ask()
```

# Understanding Code

For each of the following questions, explain what's happening in the code provided *without* adding anything to the code. Answer all parts of the question.

16. Consider the following:

```{r}
logicalVector <- c(TRUE, FALSE, FALSE, TRUE, TRUE)
mysteryVector <- logicalVector + 3
mysteryVector
```

What is the class of `mysteryVector`? Why? How are boolean values treated when used for math? Why does `mysteryVector` have the values it does?

17. Consider the following:

```{r}
vectorOne <- c(1:6)
vectorTwo <- c(1:3)
vectorOne + vectorTwo
```

Run the cell to see the result. Explain how addition of vectors of different lengths works. What terms are being added with which here? What would happen if `vectorOne` were only numbers 1-5?
